
# Features

* Look up package dependencies recursively.
* Visualize package dependencies.
* Download packages and their dependencies.
* Install downloaded packages.
* Includes a dependency solver to find a consistent set of dependencies.
* Supports CRAN and Bioconductor packages automatically.
* Supports packages on GitHub and GitLab.
* Supports packages in git repositories.
* Supports package bundles or files on the web.
* Supports local package file and trees.
* Supports the `Remotes` entry in the `DESCRIPTION` file.
* Caches metadata and downloaded packages via
  [pkgcache](https://github.com/r-lib/pkgcache)
* Performs all downloads and HTTP queries concurrently.
* Builds and installs packages in parallel.

# Install

Install the package with:

```{r}
#| eval: false
install.packages("pkgdepends")
```

If you need the development version, install it with

```{r}
#| eval: false
pak::pak("r-lib/pkgdepends")
```

# Usage

```{r}
#| eval: false
library(pkgdepends)
```

## Package references

A package reference (ref) specifies a location from which an R package
can be obtained from. Examples:

```
devtools
cran::devtools
bioc::Biobase
r-lib/pkgdepends
https://github.com/r-lib/pkgdepends
local::~/works/shiny
```

See ["Package references"][pkg_refs] for details.

## Package dependencies

Dependencies of the development version of the cli package:

```{asciicast}
#| label: deps
pd <- new_pkg_deps("r-lib/pkgcache")
pd$solve()
pd$draw()
```

See the [`pkg_deps`][pkg_deps] class for details.

## Package downloads

Downloading all dependencies of a package:

```{asciicast}
#| label: download
pdl <- new_pkg_download_proposal("r-lib/cli")
pdl$resolve()
pdl$download()
```

See the [`pkg_download_proposal`][pkg_download_proposal] class for details.

## Package installation

Installing or updating a set of package:

```{asciicast}
#| label: install
lib <- tempfile()
dir.create(lib)
pdi <- new_pkg_installation_proposal(
  "r-lib/cli",
  config = list(library = lib)
)
pdi$solve()
pdi$download()
pdi$install()
```

## Dependency resolution

[`pkg_deps`][pkg_deps], [`pkg_download_proposal`][pkg_download_proposal] and
[`pkg_installation_proposal`][pkg_installation_proposal]
all resolve their dependencies recursively, to obtain information about
all packages needed for the specified [package references][pkg_refs].
See ["Dependency resolution"][pkg_resolution] for details.

## The dependency solver

The dependency solver takes the resolution information, and works out
the exact versions of each package that must be installed, such that
version and other requirements are satisfied. See
["The dependency solver"][pkg_solution] for details.

## Installation plans

[`pkg_installation_proposal`][pkg_installation_proposal] can create
installation plans, and then also install them. It is also possible to
import installation plans that were created by other tools. See
["Installation plans"][install_plans] for details.

## Configuration

The details of [`pkg_deps`][pkg_deps],
[`pkg_download_proposal`][pkg_download_proposal] and
[`pkg_installation_proposal`][pkg_installation_proposal] can be tuned with
a list of configuration options. See ["Configuration"][pkgdepends-config] for
details.

# Related

* [pak](https://github.com/r-lib/pak) -- R package manager
* [pkgcache](https://github.com/r-lib/pkgcache) --
  Metadata and package cache
* [devtools](https://github.com/r-lib/devtools) --
  Tools for R package developers

## Code of Conduct

Please note that the pkgdepends project is released with a
[Contributor Code of Conduct](https://r-lib.github.io/pkgdepends/dev/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

# License

MIT (c) RStudio

[pkg_deps]: https://r-lib.github.io/pkgdepends/reference/pkg_deps.html
[pkg_refs]: https://r-lib.github.io/pkgdepends/reference/pkg_refs.html
[pkg_download_proposal]: https://r-lib.github.io/pkgdepends/reference/pkg_download_proposal.html
[pkg_installation_proposal]: https://r-lib.github.io/pkgdepends/reference/pkg_installation_proposal.html
[pkg_solution]: https://r-lib.github.io/pkgdepends/reference/pkg_solution.html
[pkg_resolution]: https://r-lib.github.io/pkgdepends/reference/pkg_resolution.html
[install_plans]: https://r-lib.github.io/pkgdepends/reference/install_plans.html
[pkgdepends-config]: https://r-lib.github.io/pkgdepends/reference/pkg_config.html
