
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  cache = TRUE,
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# Features

* Look up package dependencies recursively.
* Visualize package dependencies.
* Download packages and their dependencies.
* Install downloaded packages.
* Includes a dependency solver to find a consistent set of dependencies.
* Supports CRAN and Bioconductor packages automatically.
* Supports packages on GitHub.
* Supports local package file and trees.
* Supports the `Remotes` entry in the `DESCRIPTION` file.
* Caches metadata and downloaded packages via
  [pkgcache](https://github.com/r-lib/pkgcache)
* Performs all downloads and HTTP queries concurrently.
* Builds and installs packages in parallel.

# Install

```{r eval = FALSE}
install.packages("pkgdepends")
```

# Usage

```{r}
library(pkgdepends)
```

## Package references

A package reference (ref) specifies a location from which an R package
can be obtained from. Examples:

```
devtools
cran::devtools
bioc::Biobase
r-lib/pkgdepends
https://github.com/r-lib/pkgdepends
local::~/works/shiny
```

See ['Package references'][pkg_refs] for details.

## Package dependencies

Dependencies of the development version of the cli package:

```{r}
pd <- new_pkg_deps("r-lib/cli")
pd$solve()
pd$draw()
```

See [the `pkg_deps` class][pkg_deps] for details.

## Package downloads

Downloading all dependencies of a package:

```{r}
pdl <- new_pkg_download_proposal("r-lib/cli")
pdl$resolve()
pdl$download()
```

See [the `pkg_download_proposal` class][pkg_download_proposal] for details.

## Package installation

Installing or updating a set of package:

```{r}
lib <- tempfile()
pdi <- new_pkg_installation_proposal(
  "r-lib/cli",
  config = list(library = lib)
)
pdi$solve()
pdi$download()
pdi$install()
```

## Dependency resolution

[pkg_deps], [pkg_download_proposal] and [pkg_installation_proposal]
all resolve their dependencies recursively, to obtain information about
all packages needed for the specified [package references][pkg_refs].
See ['Dependency resolution'][pkg_resolution] for details.

## The dependency solver

The dependency solver takes the resolution information, and works out
the exact versions of each package that must be installed, such that
version and other requirements are satisfied. See
['The dependency solver'][pkg_solution] for details.

## Installation plans

[pkg_installation_proposal] can create installation plans, and then also
install them. It is also possible to import installation plans that were
created by other tools. See ['Installation plans'][install_plans] for
details.

## Configuration

The details of [pkg_deps], [pkg_download_proposal] and
[pkg_installation_proposal] can be tuned with a list of configuration
options. See ['Configuration'][pkg_config] for details.

# Related

* [pak](https://github.com/r-lib/pak) -- R package manager
* [pkgcache](https://github.com/r-lib/pkgcache) --
  Metadata and pacakge cache
* [devtools](https://github.com/r-lib/devtools) --
  Tools for R package developers

# License

MIT © RStudio

[pkg_refs]: TODO
[pkg_download_proposal]: TODO
[pkg_solution]: TODO
[pkg_resolution]: TODO
[pkg_config]: TODO
[install_plans]: TODO
