
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  cache = TRUE,
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# Features

* Look up package dependencies recursively.
* Visualize package dependencies.
* Download packages and their dependencies.
* Install downloaded packages.
* Includes a dependency solver to find a consistent set of dependencies.
* Supports CRAN and Bioconductor packages automatically.
* Supports packages on GitHub.
* Supports local package file and trees.
* Supports the `Remotes` entry in the `DESCRIPTION` file.
* Caches metadata and downloaded packages via
  [pkgcache](https://github.com/r-lib/pkgcache)
* Performs all downloads and HTTP queries concurrently.
* Builds and installs packages in parallel.

# Install

```{r eval = FALSE}
install.packages("pkgdepends")
```

# Usage

```{r}
library(pkgdepends)
```

## Package references

A package reference (ref) specifies a location from which an R package
can be obtained from. Examples:

```
devtools
cran::devtools
bioc::Biobase
r-lib/pkgdepends
https://github.com/r-lib/pkgdepends
local::~/works/shiny
```

See ['Package references'][pkg_refs] for details.

## Package dependencies

TODO

## Package downloads

TODO

## Package installation

TODO

## Dependency resolution

TODO

## The dependency solver

TODO

## Installation plans

TODO

## Configuration

TODO

# Related

* [pak](https://github.com/r-lib/pak) -- R package manager
* [pkgcache](https://github.com/r-lib/pkgcache) --
  Metadata and pacakge cache
* [devtools](https://github.com/r-lib/devtools) --
  Tools for R package developers

# License

MIT © RStudio

[pkg_refs]: TODO
