
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  cache = TRUE,
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

pkgdepends is a toolkit for package dependencies, downloads and
installations, to be used in other packages. If you are looking for a
package manager, see [pak](https://github.com/r-lib/pak).

# Features

* Look up package dependencies recursively.
* Visualize package dependencies.
* Download packages and their dependencies.
* Install downloaded packages.
* Includes a dependency solver to find a consistent set of dependencies.
* Supports CRAN and Bioconductor packages automatically.
* Supports packages on GitHub.
* Supports local package file and trees.
* Supports the `Remotes` entry in the `DESCRIPTION` file.
* Caches metadata and downloaded packages via
  [pkgcache](https://github.com/r-lib/pkgcache)
* Performs all downloads and HTTP queries concurrently.
* Builds and installs packages in parallel.

# Install

```{r eval = FALSE}
install.packages("pkgdepends")
```

# Usage

```{r}
library(pkgdepends)
```

## Package references

A package reference (ref) specifies a location from which an R package
can be obtained from. Examples:

For CRAN and Bioconductor packages, just use the package names, with an
optional `cran::` or `bioc::` prefix. GitHub packages are in the `user/repo`
format, or an URL to the repo. Local package files or trees use the
`local::<path>` format.

Examples:

```
devtools
cran::devtools
bioc::Biobase
r-lib/pkgdepends
https://github.com/r-lib/pkgdepends
local::~/works/shiny
```

Use [parse_pkg_refs()] to parse package references.

## Package dependencies

To query package dependencies, use 

## Package downloads

TODO

## Package installation

TODO

# Related

* [pak](https://github.com/r-lib/pak) -- R package manager
* [pkgcache](https://github.com/r-lib/pkgcache) --
  Metadata and pacakge cache
* [devtools](https://github.com/r-lib/devtools) --
  Tools for R package developers

# License

MIT © RStudio
